Refinements for open automata

### 2021-12-02 2021-Refinement/paper/refinementarticle.tex
notations in proof

\appendix
\section{Proof of transitivity}
\begin{quote}
If $\wrel{A_1}{A_2}{H}$ and $\wrel{A_2}{A_3}{H'}$, then $\wrel{A_1}{A_3}{H\cap H'}$.
\end{quote}
\proof 
Suppose we have $R_{12}$ a relation between states
of $A_1$ and of $A_2$;  Suppose we also have $R_{23}$ a relation between states of $A_2$ and of $A_3$. We build a relation between
 states of $A_1$ and of $A_3$ as follows:  for each pair of states $s_1$, $s_3$, for each state $s_2$ such that $R_{12}$ relates $s_1$ and $s_2$, and $R_{23}$ relates $s_2$ and $s_3$.
Let $R_{13}$ be the relation:\\
  $R_{13}=\{(s_1,s_3) \in S_1\times S_2 | (s_1,s_2) \in R_{12}\wedge (s_2,s_3) \in R_{23} \} $

We will show that ($R_{13}$, $H\cap H'$) is a hole-tracking simulation of $A_1$ by  $A_3$.

>>>>

\appendix
\section{Proof of transitivity}
\begin{quote}
If $\wrel{A_1}{A_2}{H}$ and $\wrel{A_2}{A_3}{H'}$, then $\wrel{A_1}{A_3}{H\cap H'}$.
\end{quote}
\proof 
If $\wrel{A_1}{A_2}{H}$ then there is $R_{12}$ a relation between states
of $A_1$ and of $A_2$;  If $\wrel{A_2}{A_3}{H'}$ then there is $R_{23}$ a relation between states of $A_2$ and of $A_3$. We build a relation between
 states of $A_1$ and of $A_3$ as follows:  for each pair of states $s_1$, $s_3$, for each state $s_2$ such that $R_{12}$ relates $s_1$ and $s_2$, and $R_{23}$ relates $s_2$ and $s_3$.
Let $R_{13}$ be the relation:\\
  $R_{13}=\{(s_1,s_3) \in S_1\times S_2 | (s_1,s_2) \in R_{12}\wedge (s_2,s_3) \in R_{23} \} $

We will show that $\wrel{A_1}{A_3}{H\cap H'}$ by exhibiting  $R_{13}$ as a hole-tracking simulation of $A_1$ by  $A_3$.
